\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}

\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% HEADER
\begin{center}
    \textbf{\Huge \scshape Saikat Das} \\ \vspace{5pt}
    \small 
    \faPhone \ +91 6202051066 \ $|$ \ 
    \faEnvelope \ \href{mailto:sd.saikat369@gmail.com}{sd.saikat369@gmail.com} \ $|$ \ 
    \faLinkedin \ \href{https://linkedin.com/in/in-saikat}{LinkedIn} \ $|$ \ 
    \faGithub \ \href{https://github.com/dis70rt}{GitHub} \ $|$ \ 
    \faCode \ \href{https://codeforces.com/profile/saikat_das}{Codeforces}
\end{center}

% EDUCATION
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology (BHU), Varanasi}{Varanasi, India}
      {Bachelor of Technology in Mining Engineering; \textbf{CGPA: 8.39/10.0}}{July 2023 to May 2027}
    \resumeSubheading
      {DPS Dhanbad}{Dhanbad, India}
      {CBSE Class XII: \textbf{87.20\%}}{2022}
  \resumeSubHeadingListEnd

% TECHNICAL SKILLS
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages}{: Go, C++, Python, Dart} \\
        \textbf{Backend Systems}{: REST APIs, Microservices, gRPC, Kafka} \\
        \textbf{Databases}{: PostgreSQL, Redis} \\
        \textbf{Tools \& Platforms}{: Flutter, Git, Docker, Linux, Postman, k6}
}}
\end{itemize}


% EXPERIENCE
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Flutter Developer Intern}{Dec 2024 to Feb 2025}
      {\href{https://www.linkedin.com/company/vrajpath-itech-llp/}{Vrajpath iTech LLP}}{Dhanbad, India}
      \resumeItemListStart
        \resumeItem{Improved application performance by changing state management and reducing API call overhead by 30\%.}
        \resumeItem{Added Google Maps SDK and Razorpay payment gateway for secure transactions.}
        \resumeItem{Fixed Play Store privacy and permission issues to meet Android 13 policies and pass the application review.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% PROJECTS
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{TradeOrders} $|$ \emph{Go, Kafka, PostgreSQL, Redis, Docker} $|$ \href{https://github.com/dis70rt/TradeOrders}{\color{blue}\underline{GitHub}}}
          {Oct 2025}
          \resumeItemListStart
            \resumeItem{Built a trade clearing engine with four microservices (API, Matching, Database, Stream) communicating through Kafka topics for order ingestion and trade execution.}
            \resumeItem{Handled 18.8k requests per second with 0\% failure rate and p95 latency of 219ms, up from 1k requests per second in the initial synchronous design. Validated with k6 load tests.}
            \resumeItem{Used Kafka key based partitioning so all orders for a given instrument go to the same partition, allowing lock free sequential matching per order book.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Bluppi} $|$ \emph{Go, gRPC, PostgreSQL, Redis, Solr, Flutter} $|$ \href{https://github.com/dis70rt/bluppi-backend}{\color{blue}\underline{Backend}} \href{https://github.com/dis70rt/bluppi-frontend}{\color{blue}\underline{Frontend}}}
          {May 2025}
          \resumeItemListStart
            \resumeItem{Built a distributed music streaming backend in Go with synchronized playback across devices using PTP style clock probing and quorum based buffer readiness.}
            \resumeItem{Wrote a presence gateway with persistent gRPC streams, tested to 51k concurrent connections with zero errors. Events fan out through Redis PubSub.}
            \resumeItem{Indexed a 500GB music catalog in Solr with field boosted search and cursor pagination. Notifications flow through Redis Streams to Firebase Cloud Messaging.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{QQL} $|$ \emph{Python, PostgreSQL} $|$ \href{https://github.com/dis70rt/qql}{\color{blue}\underline{GitHub}}}
          {Aug 2025}
          \resumeItemListStart
            \resumeItem{Built an interactive SQL shell on top of PostgreSQL with approximate query support using APPROX, ERROR, and CONFIDENCE keywords for controlled estimation.}
            \resumeItem{Runs a pilot query to determine sample size, then executes on a sample instead of full table scan. Benchmarked speed and accuracy tradeoffs across AVG, SUM, and COUNT aggregates.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{WizFlow} $|$ \emph{Python, FastAPI, Redis}}
          {Apr 2025}
          \resumeItemListStart
            \resumeItem{Built an asynchronous workflow engine with a drag and drop React interface. FastAPI backend with Redis based task queuing and real time execution logs.}
            \resumeItem{\textbf{Won 2nd Place at Nutanix Hackathon 2025}.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{SubPaper} $|$ \emph{Flutter, Go} $|$ \href{https://app.saikat.in/subpaper}{\color{blue}\underline{Play Store}}}
          {Apr 2024}
          \resumeItemListStart
            \resumeItem{Published a Flutter wallpaper app on the Play Store with over 300 downloads and a 4.5 rating.}
            \resumeItem{Pulls content from Reddit APIs and uses AdMob for monetization.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

% LEADERSHIP
\section{Leadership}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Event Executive} $|$ \emph{Club of Programmers, IIT (BHU)}}{2024 to Present}
          \resumeItemListStart
            \resumeItem{Mentored over 200 students in web and mobile development workshops.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Creative Executive} $|$ \emph{Kashiyatra, IIT (BHU)}}{2024}
          \resumeItemListStart
            \resumeItem{Improved creative presence across 9 events for Kashiyatra to increase audience engagement.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

% ACHIEVEMENTS
\section{Achievements}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Nutanix Hackathon} $|$ \emph{2nd Place}}{2025}
      \resumeProjectHeading
          {\textbf{\href{https://codeforces.com/profile/saikat_das}{Codeforces}} $|$ \emph{\href{https://codeforces.com/profile/saikat_das}{\color{blue}\underline{Pupil}} (Max Rating: \textbf{1282}), over 150 Problems Solved}}{Present}
      \resumeProjectHeading
          {\textbf{e6Data Hackathon} $|$ \emph{Special Mention}}{2024}
      \resumeProjectHeading
          {\textbf{JEE Advanced 2023} $|$ \emph{AIR 13757 (Top 9\% of qualified candidates)}}{2023}
      \resumeProjectHeading
          {\textbf{JEE Mains 2023} $|$ \emph{AIR 8166 (Top 1\% of 1.1 Million candidates)}}{2023}
    \resumeSubHeadingListEnd

\end{document}
